Why shouldn't you use numerical tests to diagnose the linear regression models?

### 2022-04-20 paper_comparison/paper_comparison/paper_comparison.Rmd
spelling of file names fixed

---
title: |
  Taylor & Francis Rmarkdown template for authors (\LaTeX\-based 
  \textsf{Interact} layout + Chicago author-date reference style)
type: ARTICLE TEMPLATE
author:
  - name: Weihao Li
    affil: a
    email: weihao.li@monash.edu
  - name: John Smith
    affil: b
    email: john.smith@uni-freiburg.de
  - name: Dominik Leutnant
    affil: c, \dagger, \ddagger
    email: leutnant@fh-muenster.de
affiliation:
  - num: a
    address: |
      Taylor & Francis, 4 Park Square, Milton Park, Abingdon, UK
  - num: b
    address: |
      Institut für Informatik, Albert-Ludwigs-Universität, Freiburg, Germany
  - num: c
    address: |
      Muenster University of Applied Sciences - 
      Institute for Infrastructure, Water, Resources, Environment,
      Correnstr. 25, 48149 Münster, Germany
bibliography: interactcadsample.bib
abstract: |
  This template is for authors who are preparing a manuscript for a Taylor & 
  Francis journal using the \LaTeX\ document preparation system and the 
  `interact} class file, which is available via selected journals' home 
  pages on the Taylor & Francis website.
keywords: |
  Sections; lists; figures; tables; mathematics; fonts; references; appendices
header-includes: |
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
output: rticles::tf_article
---

@@

Title:

>>>>

---
title: |
  Why shouldn't you use numerical tests to diagnose the linear regression models?
type: ARTICLE TEMPLATE
author:
  - name: Weihao Li
    affil: a
    email: weihao.li@monash.edu
  - name: Dianne Cook
    affil: a
    email: dicook@monash.edu
  - name: Emi Tanaka
    affil: a
    email: emi.tanaka@monash.edu
affiliation:
  - num: a
    address: |
      Department of Econometrics and Business Statistics, Monash University, Clayton, VIC, Australia
bibliography: paper.bib
abstract: |
  Abstract to fill.
keywords: |
  visual inference; model diagnostics;
header-includes: |
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
output: rticles::tf_article
---

@@

### 2022-04-20 paper_comparison/paper_comparison/paper_comparison.tex
spelling of file names fixed

\title{Taylor \& Francis Rmarkdown template for authors (\LaTeX-based
\textsf{Interact} layout + Chicago author-date reference style)}

\author{\name{Weihao Li$^{a}$, John Smith$^{b}$, Dominik Leutnant$^{c,
\dagger, \ddagger}$}
\affil{$^{a}$Taylor \& Francis, 4 Park Square, Milton Park, Abingdon,
UK; $^{b}$Institut für Informatik, Albert-Ludwigs-Universität, Freiburg,
Germany; $^{c}$Muenster University of Applied Sciences - Institute for
Infrastructure, Water, Resources, Environment, Correnstr. 25, 48149
Münster, Germany}
}

\thanks{CONTACT Weihao
Li. Email: \href{mailto:weihao.li@monash.edu}{\nolinkurl{weihao.li@monash.edu}}, John
Smith. Email: \href{mailto:john.smith@uni-freiburg.de}{\nolinkurl{john.smith@uni-freiburg.de}}, Dominik
Leutnant. Email: \href{mailto:leutnant@fh-muenster.de}{\nolinkurl{leutnant@fh-muenster.de}}}

@@

\begin{abstract}
This template is for authors who are preparing a manuscript for a Taylor
\& Francis journal using the \LaTeX~document preparation system and the
`interact\} class file, which is available via selected journals' home
pages on the Taylor \& Francis website.
\end{abstract}

>>>>

\title{Why shouldn't you use numerical tests to diagnose the linear
regression models?}

\author{\name{Weihao Li$^{a}$, Dianne Cook$^{a}$, Emi Tanaka$^{a}$}
\affil{$^{a}$Department of Econometrics and Business Statistics, Monash
University, Clayton, VIC, Australia}
}

\thanks{CONTACT Weihao
Li. Email: \href{mailto:weihao.li@monash.edu}{\nolinkurl{weihao.li@monash.edu}}, Dianne
Cook. Email: \href{mailto:dicook@monash.edu}{\nolinkurl{dicook@monash.edu}}, Emi
Tanaka. Email: \href{mailto:emi.tanaka@monash.edu}{\nolinkurl{emi.tanaka@monash.edu}}}

@@

\begin{abstract}
Abstract to fill.
\end{abstract}
